---
title: "Best %residual, pvalue < 0.01 "
author: ""
date: ''
output:  
  html_document:
    code_folding: hide
    toc: false
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, cache=FALSE, echo=FALSE}
#caching globally to decrease re-build time
knitr::opts_chunk$set(fig.align='center', cache=T, message=F,echo = FALSE)
```


```{r}
library(tidyverse)
library(plyr)
library(dplyr)
library(STASNet)
library(htmlTable)

source("./U_FUNCTIONS/Script_LinkSelection_4_ModelExtension_Pvalue_01.R")
Modeling_Dir = "/Users/sultana/PHD_PROJECT_Zeba/ANALYSIS_WORKFLOW_Oct2020_Model_MPIServer/Perc_DelRes_Highpvalue_01_20201109" 
#Modeling_Dir = "/project/ag_schulz/Zeba/MODELING_STASNet/Perc_DelRes_Highpvalue_01_20201109"

MyHTMLTheme <-  theme_set(theme_light(base_size=15))+ 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        #strip.background = element_rect(fill="grey90", colour="grey90",size=1),
        panel.background = element_rect(colour="black",size=1, fill = NA),
        # strip.text.x = element_text(color='black',margin = margin(.05, 0, .05, 0, "cm")), 
        # strip.text.y = element_text(color='black',margin = margin(.05, 0.05, .05, 0.05, "cm")),
        #axis.line = element_line(colour = 'black'), # This is used to have only the x and y axes of the plot in black.
        legend.text = element_text(size=12, margin = margin(l = 1, unit = "pt")),
        legend.title=element_text(size=15),
        legend.spacing.y = unit(0.01, 'cm'),
        #legend.key.size = unit(0.5, 'cm'),
        legend.key.size = unit(0.5, "lines"),    # key size (unit) # This controls the distance between legend icons
        legend.key.height = NULL,                # key height (unit)
        legend.key.width = NULL,                 # key width (unit)
        #legend.position = c(.95, .95),         # to place legend within the plot
       # legend.position="bottom",
        legend.justification = c("centre", "top"),
        legend.box.background = element_rect(fill=NA, colour = NA),
        legend.background=element_blank(), ### ADDED to get rid of grey bg in legend key
        #legend.box.just = "right",
        #legend.margin = margin(6, 6, 6, 6),
        axis.text.x = element_text(size=12, face = "bold"),
        axis.title.x = element_text(size=12),
        axis.text.y = element_text(size=12, face = "bold"),
        axis.title.y = element_text(size=12),
        axis.ticks = element_line(color='black'),
        strip.text.x = element_text(color='black', size=15, face="bold"),#set the size and bold face of panel headings of the facet grid.
        strip.text.y = element_text(color='black', size=15, face="bold"),# Not needed, since we dont have a facet grid panel heading on y axis
        strip.background = element_rect(colour=NA, fill=NA))



```


```{r}
# Functions :


No_rows_display=20

PrintOut_Table <- function(my_ext_list) {
  htmlTable(my_ext_list,
            align.header = "c",
            align = "c",
            col.rgroup = c("#F7F7F7","none"), # to get the stripes in alternate rows
            css.cell = rbind(rep("font-size: 1em; padding-left: 1.2em; padding-right: 1.2em;", times=ncol(my_ext_list)),
                             matrix("", ncol=ncol(my_ext_list), nrow=nrow(my_ext_list))))
}

```

Extending the models for XX and XO data, so as to keep a consensus network as far as possible.     

Steps to find the common link to be added :    
1.) Read in the extension.csv for both cell lines           
2.) Remove links from TFs and Ligands        
3.) Retain only links that have adjusted **p-value < 0.01** and value !=0      
4.) Calculate %improvement in residual for each cell line      
5.) Find the intersection list,(Links that appear in both lists)      
6.) Calculate the sum of  %improvement in residual      
7.) Order the intersection list by descending order of sum of %improvement in residual.   
8.) Add the link with Max sum of  %improvement to both models.


# {.tabset .tabset-fade}

## XX{.tabset .tabset-fade}

### Initial-Fit
```{r message = FALSE,warning=FALSE }


XX_FC_midas <- read.csv(file.path(Modeling_Dir,"XX/XX_R345.csv"))
drop_strange_cols <- c("X","X1")## Removing two strange columns that somehow creep into the MIDAS files when it is saved as csv.
XX_FC_midas <- XX_FC_midas[!colnames(XX_FC_midas) %in% drop_strange_cols] 

# My_dir <- "/Users/sultana/PHD_PROJECT_Zeba/ANALYSIS_PIPIELINE_MPIserver/S4_Merge_BP_WB_FC_Aktvalues"
# XX_FC_R5onlydropped <- read.csv(file.path(My_dir,"R345_XX_BP_WB_Merged_MIDAS_bCateninNO_AktFiltered.csv"))

```


```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

Init_XX_FC_Model_Folder = "XX/run_XX_R345_Network_100k_2020-11-09" #Current_Model_Folder
Init_XX_FC_Model = "XX_R345_Network_100k+pl.mra"
Init_XX_FC_Ext_File = "extension_XX_R345_Network_100k+pl+red.csv"

Init_XX_FC_model = rebuildModel(file.path(Modeling_Dir,Init_XX_FC_Model_Folder,Init_XX_FC_Model), XX_FC_midas)
plotModelGraph(Init_XX_FC_model)
#plotModelParameters(Init_XX_FC_model) 

```

Model residual = `r round(Init_XX_FC_model$bestfit)`     

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36 , fig.height=12, out.extra='style=""'}

plotModelAccuracy(Init_XX_FC_model)
#plotModelScores(Init_XX_FC_model)
```

Link Extension :     
```{r}

Init_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,Init_XX_FC_Model_Folder,Init_XX_FC_Ext_File), sep = "\t", header = TRUE)
#Init_XX_FC_LinkSugg <- Init_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(Init_XX_FC_LinkSugg,n=No_rows_display))

```

### LA1:Jak -> Fgfr
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA1_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA1_100k_2020-11-09" #Current_Model_Folder
LA1_XX_FC_Model = "XX_R345_Network_LA1_100k.mra"
LA1_XX_FC_Ext_File = "extension_XX_R345_Network_LA1_100k+red.csv"

LA1_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA1_XX_FC_Model_Folder,LA1_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA1_XX_FC_model)
#plotModelParameters(LA1_XX_FC_model) 

```

Model residual = `r round(LA1_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA1_XX_FC_model)
plotModelScores(LA1_XX_FC_model)

```

Link Extension :     
```{r}

LA1_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA1_XX_FC_Model_Folder,LA1_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA1_XX_FC_LinkSugg <- LA1_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA1_XX_FC_LinkSugg,n=No_rows_display))

```


### LA2:Gsk3->Igfr
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA2_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA2_100k_2020-11-09" #Current_Model_Folder
LA2_XX_FC_Model = "XX_R345_Network_LA2_100k.mra"
LA2_XX_FC_Ext_File = "extension_XX_R345_Network_LA2_100k+red.csv"

LA2_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA2_XX_FC_Model_Folder,LA2_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA2_XX_FC_model)
#plotModelParameters(LA2_XX_FC_model) 

```

Model residual = `r round(LA2_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA2_XX_FC_model)
plotModelScores(LA2_XX_FC_model)

```

Link Extension :     
```{r}

LA2_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA2_XX_FC_Model_Folder,LA2_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA2_XX_FC_LinkSugg <- LA2_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA2_XX_FC_LinkSugg,n=No_rows_display))

```


### LA3:Erk->Mek

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA3_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA3_100k_2020-11-09" #Current_Model_Folder
LA3_XX_FC_Model = "XX_R345_Network_LA3_100k.mra"
LA3_XX_FC_Ext_File = "extension_XX_R345_Network_LA3_100k+red.csv"

LA3_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA3_XX_FC_Model_Folder,LA3_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA3_XX_FC_model)
#plotModelParameters(LA3_XX_FC_model) 

```

Model residual = `r round(LA3_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA3_XX_FC_model)
plotModelScores(LA3_XX_FC_model)

```

Link Extension :     
```{r}

LA3_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA3_XX_FC_Model_Folder,LA3_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA3_XX_FC_LinkSugg <- LA3_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA3_XX_FC_LinkSugg,n=No_rows_display))

```


### LA4:Bmp4r->Fgfr
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA4_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA4_100k_2020-11-09" #Current_Model_Folder
LA4_XX_FC_Model = "XX_R345_Network_LA4_100k.mra"
LA4_XX_FC_Ext_File = "extension_XX_R345_Network_LA4_100k+red.csv"

LA4_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA4_XX_FC_Model_Folder,LA4_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA4_XX_FC_model)
#plotModelParameters(LA4_XX_FC_model) 

```

Model residual = `r round(LA4_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA4_XX_FC_model)
plotModelScores(LA4_XX_FC_model)

```

Link Extension :     
```{r}

LA4_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA4_XX_FC_Model_Folder,LA4_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA4_XX_FC_LinkSugg <- LA4_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA4_XX_FC_LinkSugg,n=No_rows_display))
```


### LA5:Jak->Gsk3
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA5_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA5_100k_2020-11-09" #Current_Model_Folder
LA5_XX_FC_Model = "XX_R345_Network_LA5_100k.mra"
LA5_XX_FC_Ext_File = "extension_XX_R345_Network_LA5_100k+red.csv"

LA5_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA5_XX_FC_Model_Folder,LA5_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA5_XX_FC_model)
#plotModelParameters(LA5_XX_FC_model) 

```

Model residual = `r round(LA5_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA5_XX_FC_model)
plotModelScores(LA5_XX_FC_model)

```

Link Extension :     
```{r}

LA5_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA5_XX_FC_Model_Folder,LA5_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA5_XX_FC_LinkSugg <- LA5_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA5_XX_FC_LinkSugg,n=No_rows_display))

```


### LA6:Bmp4r->Smad2
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA6_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA6_100k_2020-11-10" #Current_Model_Folder
LA6_XX_FC_Model = "XX_R345_Network_LA6_100k.mra"
LA6_XX_FC_Ext_File = "extension_XX_R345_Network_LA6_100k+red.csv"

LA6_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA6_XX_FC_Model_Folder,LA6_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA6_XX_FC_model)
#plotModelParameters(LA6_XX_FC_model) 

```

Model residual = `r round(LA6_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA6_XX_FC_model)
plotModelScores(LA6_XX_FC_model)

```

Link Extension :     
```{r}

LA6_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA6_XX_FC_Model_Folder,LA6_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA6_XX_FC_LinkSugg <- LA6_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA6_XX_FC_LinkSugg,n=No_rows_display))

```


### LA7:Actr->Ras
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA7_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA7_100k_2020-11-10" #Current_Model_Folder
LA7_XX_FC_Model = "XX_R345_Network_LA7_100k.mra"
LA7_XX_FC_Ext_File = "extension_XX_R345_Network_LA7_100k+red.csv"

LA7_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA7_XX_FC_Model_Folder,LA7_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA7_XX_FC_model)
#plotModelParameters(LA7_XX_FC_model) 

```

Model residual = `r round(LA7_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA7_XX_FC_model)
plotModelScores(LA7_XX_FC_model)

```

Link Extension :     
```{r}

LA7_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA7_XX_FC_Model_Folder,LA7_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA7_XX_FC_LinkSugg <- LA7_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA7_XX_FC_LinkSugg,n=No_rows_display))

```

### LA8:Gsk3->Stat3

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA8_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA8_100k_2020-11-10" #Current_Model_Folder
LA8_XX_FC_Model = "XX_R345_Network_LA8_100k.mra"
LA8_XX_FC_Ext_File = "extension_XX_R345_Network_LA8_100k+red.csv"

LA8_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA8_XX_FC_Model_Folder,LA8_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA8_XX_FC_model)
#plotModelParameters(LA8_XX_FC_model) 

```

Model residual = `r round(LA8_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA8_XX_FC_model)
plotModelScores(LA8_XX_FC_model)

```

Link Extension :     
```{r}

LA8_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA8_XX_FC_Model_Folder,LA8_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA8_XX_FC_LinkSugg <- LA8_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA8_XX_FC_LinkSugg,n=No_rows_display))

```



### LA9:Lifr->Gsk3

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA9_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA9_100k_2020-11-10" #Current_Model_Folder
LA9_XX_FC_Model = "XX_R345_Network_LA9_100k.mra"
LA9_XX_FC_Ext_File = "extension_XX_R345_Network_LA9_100k+red.csv"

LA9_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA9_XX_FC_Model_Folder,LA9_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA9_XX_FC_model)
#plotModelParameters(LA9_XX_FC_model) 

```

Model residual = `r round(LA9_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA9_XX_FC_model)
plotModelScores(LA9_XX_FC_model)

```

Link Extension :     
```{r}

LA9_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA9_XX_FC_Model_Folder,LA9_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA9_XX_FC_LinkSugg <- LA9_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA9_XX_FC_LinkSugg,n=No_rows_display))

```


### LA10:Jak->Bmp4r
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA10_XX_FC_Model_Folder = "XX/run_XX_R345_Network_LA10_100k_2020-11-10" #Current_Model_Folder
LA10_XX_FC_Model = "XX_R345_Network_LA10_100k.mra"
LA10_XX_FC_Ext_File = "extension_XX_R345_Network_LA10_100k+red.csv"

LA10_XX_FC_model = rebuildModel(file.path(Modeling_Dir,LA10_XX_FC_Model_Folder,LA10_XX_FC_Model), XX_FC_midas)
plotModelGraph(LA10_XX_FC_model)
#plotModelParameters(LA10_XX_FC_model) 

```

Model residual = `r round(LA10_XX_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA10_XX_FC_model)
plotModelScores(LA10_XX_FC_model)

```

Link Extension :     
```{r}

LA10_XX_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA10_XX_FC_Model_Folder,LA10_XX_FC_Ext_File), sep = "\t", header = TRUE)
#LA10_XX_FC_LinkSugg <- LA10_XX_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA10_XX_FC_LinkSugg,n=No_rows_display))

```


## XO{.tabset .tabset-fade}

### Initial-Fit
```{r message = FALSE,warning=FALSE }

XO_FC_midas <- read.csv(file.path(Modeling_Dir,"XO/XO_R345.csv"))
drop_strange_cols <- c("X","X1")## Removing two strange columns that somehow creep into the MIDAS files when it is saved as csv.
XO_FC_midas <- XO_FC_midas[!colnames(XO_FC_midas) %in% drop_strange_cols] 

# My_dir <- "/Users/sultana/PHD_PROJECT_Zeba/ANALYSIS_PIPIELINE_MPIserver/S4_Merge_BP_WB_FC_Aktvalues"
# XO_FC_R5onlydropped <- read.csv(file.path(My_dir,"R345_XO_BP_WB_Merged_MIDAS_bCateninNO_AktFiltered.csv"))

```


```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

Init_XO_FC_Model_Folder = "XO/run_XO_R345_Network_100k_2020-11-09" #Current_Model_Folder
Init_XO_FC_Model = "XO_R345_Network_100k+pl.mra"
Init_XO_FC_Ext_File = "extension_XO_R345_Network_100k+pl+red.csv"

Init_XO_FC_model = rebuildModel(file.path(Modeling_Dir,Init_XO_FC_Model_Folder,Init_XO_FC_Model), XO_FC_midas)
plotModelGraph(Init_XO_FC_model)
#plotModelParameters(Init_XO_FC_model) 

```

Model residual = `r round(Init_XO_FC_model$bestfit)`     

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}
plotModelAccuracy(Init_XO_FC_model)
plotModelScores(Init_XO_FC_model)
```

Link Extension :     
```{r}

Init_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,Init_XO_FC_Model_Folder,Init_XO_FC_Ext_File), sep = "\t", header = TRUE)
#Init_XO_FC_LinkSugg <- Init_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(Init_XO_FC_LinkSugg,n=No_rows_display))


```

### LA1:Jak -> Fgfr
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA1_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA1_100k_2020-11-09" #Current_Model_Folder
LA1_XO_FC_Model = "XO_R345_Network_LA1_100k.mra"
LA1_XO_FC_Ext_File = "extension_XO_R345_Network_LA1_100k+red.csv"

LA1_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA1_XO_FC_Model_Folder,LA1_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA1_XO_FC_model)
#plotModelParameters(LA1_XO_FC_model) 

```

Model residual = `r round(LA1_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA1_XO_FC_model)
plotModelScores(LA1_XO_FC_model)

```

Link Extension :     
```{r}

LA1_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA1_XO_FC_Model_Folder,LA1_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA1_XO_FC_LinkSugg <- LA1_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA1_XO_FC_LinkSugg,n=No_rows_display))

```




### LA2:Gsk3->Igfr
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA2_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA2_100k_2020-11-09" #Current_Model_Folder
LA2_XO_FC_Model = "XO_R345_Network_LA2_100k.mra"
LA2_XO_FC_Ext_File = "extension_XO_R345_Network_LA2_100k+red.csv"

LA2_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA2_XO_FC_Model_Folder,LA2_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA2_XO_FC_model)
#plotModelParameters(LA2_XO_FC_model) 

```

Model residual = `r round(LA2_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA2_XO_FC_model)
plotModelScores(LA2_XO_FC_model)

```

Link Extension :     
```{r}

LA2_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA2_XO_FC_Model_Folder,LA2_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA2_XO_FC_LinkSugg <- LA2_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA2_XO_FC_LinkSugg,n=No_rows_display))

```


### LA3:Erk->Mek
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA3_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA3_100k_2020-11-09" #Current_Model_Folder
LA3_XO_FC_Model = "XO_R345_Network_LA3_100k.mra"
LA3_XO_FC_Ext_File = "extension_XO_R345_Network_LA3_100k+red.csv"

LA3_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA3_XO_FC_Model_Folder,LA3_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA3_XO_FC_model)
#plotModelParameters(LA3_XO_FC_model) 

```

Model residual = `r round(LA3_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA3_XO_FC_model)
plotModelScores(LA3_XO_FC_model)

```

Link Extension :     
```{r}

LA3_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA3_XO_FC_Model_Folder,LA3_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA3_XO_FC_LinkSugg <- LA3_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA3_XO_FC_LinkSugg,n=No_rows_display))

```


### LA4:Bmp4r->Fgfr
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA4_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA4_100k_2020-11-09" #Current_Model_Folder
LA4_XO_FC_Model = "XO_R345_Network_LA4_100k.mra"
LA4_XO_FC_Ext_File = "extension_XO_R345_Network_LA4_100k+red.csv"

LA4_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA4_XO_FC_Model_Folder,LA4_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA4_XO_FC_model)
#plotModelParameters(LA4_XO_FC_model) 

```

Model residual = `r round(LA4_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA4_XO_FC_model)
plotModelScores(LA4_XO_FC_model)

```

Link Extension :     
```{r}

LA4_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA4_XO_FC_Model_Folder,LA4_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA4_XO_FC_LinkSugg <- LA4_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA4_XO_FC_LinkSugg,n=No_rows_display))

```


### LA5:Jak	->Gsk3
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA5_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA5_100k_2020-11-09" #Current_Model_Folder
LA5_XO_FC_Model = "XO_R345_Network_LA5_100k.mra"
LA5_XO_FC_Ext_File = "extension_XO_R345_Network_LA5_100k+red.csv"

LA5_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA5_XO_FC_Model_Folder,LA5_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA5_XO_FC_model)
#plotModelParameters(LA5_XO_FC_model) 

```

Model residual = `r round(LA5_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA5_XO_FC_model)
plotModelScores(LA5_XO_FC_model)

```

Link Extension :     
```{r}

LA5_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA5_XO_FC_Model_Folder,LA5_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA5_XO_FC_LinkSugg <- LA5_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA5_XO_FC_LinkSugg,n=No_rows_display))

```


### LA6:Bmp4r->Smad2
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA6_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA6_100k_2020-11-10" #Current_Model_Folder
LA6_XO_FC_Model = "XO_R345_Network_LA6_100k.mra"
LA6_XO_FC_Ext_File = "extension_XO_R345_Network_LA6_100k+red.csv"

LA6_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA6_XO_FC_Model_Folder,LA6_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA6_XO_FC_model)
#plotModelParameters(LA6_XO_FC_model) 

```

Model residual = `r round(LA6_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA6_XO_FC_model)
plotModelScores(LA6_XO_FC_model)

```

Link Extension :     
```{r}

LA6_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA6_XO_FC_Model_Folder,LA6_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA6_XO_FC_LinkSugg <- LA6_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA6_XO_FC_LinkSugg,n=No_rows_display))
```


### LA7:Actr->Ras
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA7_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA7_100k_2020-11-10" #Current_Model_Folder
LA7_XO_FC_Model = "XO_R345_Network_LA7_100k.mra"
LA7_XO_FC_Ext_File = "extension_XO_R345_Network_LA7_100k+red.csv"

LA7_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA7_XO_FC_Model_Folder,LA7_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA7_XO_FC_model)
#plotModelParameters(LA7_XO_FC_model) 

```

Model residual = `r round(LA7_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA7_XO_FC_model)
plotModelScores(LA7_XO_FC_model)

```

Link Extension :     
```{r}

LA7_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA7_XO_FC_Model_Folder,LA7_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA7_XO_FC_LinkSugg <- LA7_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA7_XO_FC_LinkSugg,n=No_rows_display))

```

### LA8:Gsk3->Stat3
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA8_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA8_100k_2020-11-10" #Current_Model_Folder
LA8_XO_FC_Model = "XO_R345_Network_LA8_100k.mra"
LA8_XO_FC_Ext_File = "extension_XO_R345_Network_LA8_100k+red.csv"

LA8_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA8_XO_FC_Model_Folder,LA8_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA8_XO_FC_model)
#plotModelParameters(LA8_XO_FC_model) 

```

Model residual = `r round(LA8_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA8_XO_FC_model)
plotModelScores(LA8_XO_FC_model)

```

Link Extension :     
```{r}

LA8_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA8_XO_FC_Model_Folder,LA8_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA8_XO_FC_LinkSugg <- LA8_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA8_XO_FC_LinkSugg,n=No_rows_display))

```



### LA9:Lifr->Gsk3
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA9_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA9_100k_2020-11-10" #Current_Model_Folder
LA9_XO_FC_Model = "XO_R345_Network_LA9_100k.mra"
LA9_XO_FC_Ext_File = "extension_XO_R345_Network_LA9_100k+red.csv"

LA9_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA9_XO_FC_Model_Folder,LA9_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA9_XO_FC_model)
#plotModelParameters(LA9_XO_FC_model) 

```

Model residual = `r round(LA9_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA9_XO_FC_model)
plotModelScores(LA9_XO_FC_model)

```

Link Extension :     
```{r}

LA9_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA9_XO_FC_Model_Folder,LA9_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA9_XO_FC_LinkSugg <- LA9_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA9_XO_FC_LinkSugg,n=No_rows_display))

```

### LA10:Jak->Bmp4r
```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,550), fig.height=6, out.extra='style=""'}

LA10_XO_FC_Model_Folder = "XO/run_XO_R345_Network_LA10_100k_2020-11-10" #Current_Model_Folder
LA10_XO_FC_Model = "XO_R345_Network_LA10_100k.mra"
LA10_XO_FC_Ext_File = "extension_XO_R345_Network_LA10_100k+red.csv"

LA10_XO_FC_model = rebuildModel(file.path(Modeling_Dir,LA10_XO_FC_Model_Folder,LA10_XO_FC_Model), XO_FC_midas)
plotModelGraph(LA10_XO_FC_model)
#plotModelParameters(LA10_XO_FC_model) 

```

Model residual = `r round(LA10_XO_FC_model$bestfit)` 

```{r echo=FALSE, message = FALSE,warning=FALSE, out.width=c(350,350), dpi=36, fig.height=12, out.extra='style=""'}

plotModelAccuracy(LA10_XO_FC_model)
plotModelScores(LA10_XO_FC_model)

```

Link Extension :     
```{r}

LA10_XO_FC_LinkSugg = read.table(file.path(Modeling_Dir,LA10_XO_FC_Model_Folder,LA10_XO_FC_Ext_File), sep = "\t", header = TRUE)
#LA10_XO_FC_LinkSugg <- LA10_XO_FC_LinkSugg[c(1:20),-1]
PrintOut_Table(head(LA10_XO_FC_LinkSugg,n=No_rows_display))

```


## Link_Selection{.tabset .tabset-fade}
### Init
**XX : List post filter**
```{r}

INIT_XX_ext <- filter_ext_list(Init_XX_FC_LinkSugg)
PrintOut_Table(head(INIT_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

INIT_XO_ext <- filter_ext_list(Init_XO_FC_LinkSugg)
PrintOut_Table(head(INIT_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

INIT_common_links_byTot_Percentage_DelResidual <- Select_Link(INIT_XX_ext,INIT_XO_ext,3)
PrintOut_Table(head(INIT_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```

### LA1
**XX : List post filter**
```{r}

LA1_XX_ext <- filter_ext_list(LA1_XX_FC_LinkSugg)
PrintOut_Table(head(LA1_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA1_XO_ext <- filter_ext_list(LA1_XO_FC_LinkSugg)
PrintOut_Table(head(LA1_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA1_common_links_byTot_Percentage_DelResidual <- Select_Link(LA1_XX_ext,LA1_XO_ext,3)
PrintOut_Table(head(LA1_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA2
**XX : List post filter**
```{r}

LA2_XX_ext <- filter_ext_list(LA2_XX_FC_LinkSugg)
PrintOut_Table(head(LA2_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA2_XO_ext <- filter_ext_list(LA2_XO_FC_LinkSugg)
PrintOut_Table(head(LA2_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA2_common_links_byTot_Percentage_DelResidual <- Select_Link(LA2_XX_ext,LA2_XO_ext,3)
PrintOut_Table(head(LA2_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA3
**XX : List post filter**
```{r}

LA3_XX_ext <- filter_ext_list(LA3_XX_FC_LinkSugg)
PrintOut_Table(head(LA3_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA3_XO_ext <- filter_ext_list(LA3_XO_FC_LinkSugg)
PrintOut_Table(head(LA3_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA3_common_links_byTot_Percentage_DelResidual <- Select_Link(LA3_XX_ext,LA3_XO_ext,3)
PrintOut_Table(head(LA3_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA4
**XX : List post filter**
```{r}

LA4_XX_ext <- filter_ext_list(LA4_XX_FC_LinkSugg)
PrintOut_Table(head(LA4_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA4_XO_ext <- filter_ext_list(LA4_XO_FC_LinkSugg)
PrintOut_Table(head(LA4_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA4_common_links_byTot_Percentage_DelResidual <- Select_Link(LA4_XX_ext,LA4_XO_ext,3)
PrintOut_Table(head(LA4_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA5
**XX : List post filter**
```{r}

LA5_XX_ext <- filter_ext_list(LA5_XX_FC_LinkSugg)
PrintOut_Table(head(LA5_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA5_XO_ext <- filter_ext_list(LA5_XO_FC_LinkSugg)
PrintOut_Table(head(LA5_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA5_common_links_byTot_Percentage_DelResidual <- Select_Link(LA5_XX_ext,LA5_XO_ext,3)
PrintOut_Table(head(LA5_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA6
**XX : List post filter**
```{r}

LA6_XX_ext <- filter_ext_list(LA6_XX_FC_LinkSugg)
PrintOut_Table(head(LA6_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA6_XO_ext <- filter_ext_list(LA6_XO_FC_LinkSugg)
PrintOut_Table(head(LA6_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA6_common_links_byTot_Percentage_DelResidual <- Select_Link(LA6_XX_ext,LA6_XO_ext,3)
PrintOut_Table(head(LA6_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA7
**XX : List post filter**
```{r}

LA7_XX_ext <- filter_ext_list(LA7_XX_FC_LinkSugg)
PrintOut_Table(head(LA7_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA7_XO_ext <- filter_ext_list(LA7_XO_FC_LinkSugg)
PrintOut_Table(head(LA7_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA7_common_links_byTot_Percentage_DelResidual <- Select_Link(LA7_XX_ext,LA7_XO_ext,3)
PrintOut_Table(head(LA7_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


### LA8
**XX : List post filter**
```{r}

LA8_XX_ext <- filter_ext_list(LA8_XX_FC_LinkSugg)
PrintOut_Table(head(LA8_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA8_XO_ext <- filter_ext_list(LA8_XO_FC_LinkSugg)
PrintOut_Table(head(LA8_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA8_common_links_byTot_Percentage_DelResidual <- Select_Link(LA8_XX_ext,LA8_XO_ext,3)
PrintOut_Table(head(LA8_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```




### LA9
**XX : List post filter**
```{r}

LA9_XX_ext <- filter_ext_list(LA9_XX_FC_LinkSugg)
PrintOut_Table(head(LA9_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA9_XO_ext <- filter_ext_list(LA9_XO_FC_LinkSugg)
PrintOut_Table(head(LA9_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

LA9_common_links_byTot_Percentage_DelResidual <- Select_Link(LA9_XX_ext,LA9_XO_ext,3)
PrintOut_Table(head(LA9_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```

### LA10
**XX : List post filter**
```{r}

#LA10_XX_ext <- filter_ext_list(LA10_XX_FC_LinkSugg)
#PrintOut_Table(head(LA10_XX_ext, n=No_rows_display))

```

**XO : List post filter**
```{r}

LA10_XO_ext <- filter_ext_list(LA10_XO_FC_LinkSugg)
PrintOut_Table(head(LA10_XO_ext, n=No_rows_display))
```

**Intersection List**
```{r}

# LA10_common_links_byTot_Percentage_DelResidual <- Select_Link(LA10_XX_ext,LA10_XO_ext,3)
# PrintOut_Table(head(LA10_common_links_byTot_Percentage_DelResidual, n=No_rows_display))

```


## Summary

**Links Added and Residuals**

```{r message = FALSE, out.width=c(350,350), fig.height=5, fig.show='hold', out.extra='style=""'}

Final_Network_file <- "XX/Network_LA10.tab"
Final_Network = read.csv(file.path(Modeling_Dir,Final_Network_file), sep = "\t", header = FALSE)
colnames(Final_Network) <- c("from_node","to_node")
New_links <- Final_Network[18:nrow(Final_Network),]
New_links <- New_links %>% 
  unite("Link",from_node:to_node,remove = FALSE )
New_links$Link <- gsub("_","->",New_links$Link)

Model_iteration=c("Init","1","2","3","4","5","6","7","8", "9","10")
Model_iteration = factor(Model_iteration, levels =Model_iteration )

LinksAdded_p_01<- data.frame(Iteration=Model_iteration,Links=c("Init Network",New_links$Link))



```


```{r}

res_p_01_XX = c(Init_XX_FC_model$bestfit,
                LA1_XX_FC_model$bestfit,
                LA2_XX_FC_model$bestfit,
                LA3_XX_FC_model$bestfit,
                LA4_XX_FC_model$bestfit,
                LA5_XX_FC_model$bestfit,
                LA6_XX_FC_model$bestfit,
                LA7_XX_FC_model$bestfit,
                LA8_XX_FC_model$bestfit,
                LA9_XX_FC_model$bestfit,
                LA10_XX_FC_model$bestfit)

res_p_01_XO = c(Init_XO_FC_model$bestfit,
                LA1_XO_FC_model$bestfit,
                LA2_XO_FC_model$bestfit,
                LA3_XO_FC_model$bestfit,
                LA4_XO_FC_model$bestfit,
                LA5_XO_FC_model$bestfit,
                LA6_XO_FC_model$bestfit,
                LA7_XO_FC_model$bestfit,
                LA8_XO_FC_model$bestfit,
                LA9_XO_FC_model$bestfit,
                LA10_XO_FC_model$bestfit)

Links_Residuals_p_01 <- data.frame(Model_iteration,Links=c("Init Network",New_links$Link),res_p_01_XX,res_p_01_XO)
Links_Residuals_p_01 <- Links_Residuals_p_01 %>% 
  dplyr::mutate(res_p_01_XX=round(res_p_01_XX,2),
                res_p_01_XO=round(res_p_01_XO,2))
write.csv(Links_Residuals_p_01, "Links_Residuals_p_01.csv")

PrintOut_Table(Links_Residuals_p_01)


Res_p_01_long <- Links_Residuals_p_01 %>% 
  pivot_longer(grep("res",colnames(Links_Residuals_p_01)),names_to = "Model", values_to = "residual")


MyCellLineColours <- c("XX" = "#fddbc7", 
                       "res_p_05_XX" = "#f4a582", 
                       "res_p_01_XX" = "#d6604d",
                       "res_p_005_XX" = "#b2182b",
                       "res_p_001_XX" = "#67001f",
                       
                       "XO" = "#d1e5f0",
                       "res_p_05_XO" = "#92c5de",
                       "res_p_01_XO" = "#4393c3",
                       "res_p_005_XO" = "#2166ac",
                       "res_p_001_XO" = "#053061")


p <- ggplot(Res_p_01_long, aes(x=Model_iteration, y=residual, color=Model, group=Model))+
  MyHTMLTheme+
  geom_point(size=4)+
  geom_line(size=1.5)+
  scale_color_manual(values = MyCellLineColours)+
  labs(x = "Model Extension : Iteration number",
       y = "Model Residual\n")+
  ylim(0,NA)+
  geom_hline(yintercept=371, linetype="dashed", color = "black")+
  theme(text=element_text(size = 16,color = "grey10"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 22))

print(p)

```

